Limitations on the Two-Infall Scenario in the Era of Large Stellar Age Catalogs

### 2025-04-01 src/tex/ms.tex

\begin{abstract}
    Stellar populations in the Milky Way exhibit a clear separation into two chemically distinct populations that are separated by their [$\alpha$/Fe] ratios. A popular explanation for this observation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy. However, most previous studies using the two-infall scenario have explored a limited portion of the parameter space, typically neglecting radial migration and assuming that the Galactic disk never ejected a substantial outflow. Thanks to advances in stellar age measurements in recent years, we can now also compare this popular model to more direct measurements of the Galaxy's evolutionary timescales from large stellar catalogs. We run multi-zone galactic chemical evolution (GCE) models with a two-infall-driven star formation history, radially dependent mass-loaded outflows, and a prescription for radial migration tuned to a hydrodynamic simulation. We compare our model results to abundance patterns across the disk from APOGEE DR17 and early data from the SDSS-V Milky Way Mapper program, supplemented with stellar age estimates through multiple methods. Although the two-infall scenario offers a natural explanation for the [$\alpha$/Fe] bimodality, it struggles to explain several features of the age--abundances structure in the disk. The two-infall scenario generically predicts a massive and long-lasting dilution event, but the data show that stellar metallicity is remarkably constant with age across much of the Galactic disk. This apparent age-independence places considerable restrictions upon the two-infall parameter space. These issues can be mitigated, but not completely resolved, by allowing the accreted gas to be pre-enriched to low metallicity.
\end{abstract}

@@

% \todo{Hook, summary of alpha-bimodality.}
Studies of galactic chemical evolution (GCE) aim to explain observed stellar abundance patterns by modeling the star formation history of the Milky Way. A long-standing paradigm of GCE has been that the metallicity of the interstellar medium (ISM) increases over time due to supernova enrichment from successive generations of stars. In this view, one feature of the Milky Way disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}. The high-$\alpha$ sequence consists of old stars \citep[$\sim9$ Gyr;][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe and is associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, with approximately Solar \aFe, and is associated with the thin disk. The $\alpha$-bimodality is present across the Galactic disk, but the relative strength of the high- and low-$\alpha$ sequences varies by location \citep{hayden_chemical_2015}.

% Summary of two-infall literature
The two-infall model of chemical evolution was proposed by \citet{chiappini_chemical_1997} to explain the origin of the thick and thin disks. Though the model has been revised and refined since, the basic premise remains the same: the rate of gas infall onto the Galaxy is described by two consecutive, exponentially declining bursts. The relatively low infall rate between the two bursts leads to a hiatus in the star formation rate, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences without producing many stars in between. 
% By varying the timescale of the second infall, the model can produce inside-out disk growth and a radial abundance gradient.
The initial model of \citet{chiappini_chemical_1997} successfully reproduced the available abundance data at the time, which were largely confined to the Solar neighborhood.

Subsequent studies refined the two-infall model to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, and others have explored in its context the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, a variable star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations due to spiral modes \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}. Recently, \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the inferred star formation history from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and explain the recent abundance evolution of the Solar neighborhood.

\todo{Observational evidence other than $\alpha$-bimodality.} \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}. \citet{nataf_accurate_2024} also observe multiple sequences in the age--metallicity relation in their sample of $\sim400,000$ local subgiants, although the break between them is not as clean as in \citet{nissen_high-precision_2020}. \citet{chen_recent_2025} however argue that this trend can be explained by a smooth star formation history with inside-out growth: the older sequence consists of stars which have migrated from the inner galaxy, where the star formation rate peaked early, while the younger sequence was formed locally.

@@

\todo{Goal and summary of paper.}

@@

The infall rate is described by two successive, exponentially declining bursts in time. The first infall component induces the formation of the thick disk, and the second component produces the thin disk. At a given galactocentric radius $R_{\rm gal}$, the un-normalized form of the infall rate is
\begin{equation}
    \label{eq:twoinfall-ifr}
    f_{\rm in}(t|R_{\rm gal}) = e^{-t/\tau_1} + f_{2/1}(R_{\rm gal}) e^{-(t-t_{\rm max})/\tau_2},
\end{equation}
where $\tau_1$ and $\tau_2$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall and thus the time of maximum gas infall, and $f_{2/1}$ is the ratio of the second infall amplitude to the first. We calculate $f_{2/1}$ for each zone such that the resulting stellar density profile follows a two-component disk, with the surface density ratio of the thick and thin disks given by
\begin{equation}
    f_\Sigma(R) \equiv \frac{\Sigma_1(R)}{\Sigma_2(R)} = f_{\Sigma,0} e^{R(1/R_2 - 1/R_1)}.
\end{equation}
We adopt a thick disk scale radius of $R_1=2.0\,{\rm kpc}$, a thin disk scale radius of $R_2=2.5\,{\rm kpc}$, and a central surface density ratio of $f_{\Sigma,0}=0.27$ \citep{bland-hawthorn_galaxy_2016}. In the Solar neighborhood, this produces a thick-to-thin disk mass ratio of $f_\Sigma(R_\odot)=0.12$. By comparison, \citet{mackereth_age-metallicity_2017} finds $f_\Sigma(R_\odot)=0.18\pm0.05$ from APOGEE. \todo{Compare with other two-infall papers, which generally have a higher thick-to-thin ratio.} \citet{spitoni_galactic_2020} explores $f_\Sigma(R_\odot)\approx0.23-0.31$, \citet{palla_chemical_2020} assumes $f_\Sigma(R_\odot)=0.23$, \citet{spitoni_apogee_2021} derives $f_\Sigma(R_\odot)=0.18$ (again from APOGEE), \citet{spitoni_remind_2024} assumes $f_\Sigma(R_\odot)=0.4$.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_params.pdf}
    \caption{Stellar [O/Fe] distributions produced by select multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e). The layout is similar to Figure \ref{fig:abundance-evolution-yields}. Each column shows results from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$ (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.48$. {\bf Key takeaway:} For the \yZ{2} case, pre-enrichment of the accreted gas or a higher thick-to-thin disk ratio can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.}
    \label{fig:ofe-distribution-parameters}
\end{figure*}

The two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence. Figure \ref{fig:ofe-df} compares [O/Fe] distributions across the Galactic disk produced by four different multi-zone models with the distributions observed in APOGEE DR17. For the fiducial model (a) with $y/Z_\odot=1$, the latter two peaks are close together and the overall effect is similar to the observed distribution. With a higher yield set, however, there is a $\sim0.2$ dex separation between the low- and intermediate-$\alpha$ peaks, because the CCSN element production after the second infall is more efficient. As a result, model (b) predicts a high density of stars in the APOGEE ``trough.''

In columns (c) and (d) of Figure \ref{fig:ofe-df}, we attempt to mitigate the issue of the intermediate-$\alpha$ peak for the $y/Z_\odot=2$ yield set. Model (c) switches out our fiducial DTD with a power-law DTD, which decreases the timescale for Fe production. However, as shown by \citet{dubay_galactic_2024}, models with a power-law DTD struggle to reproduce the high-$\alpha$ sequence for a wide range of star formation histories, and the results are no different for this two-infall model.

Finally, in model (d) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.7$ at late times. We choose this value because it is the maximum which can plausibly still reproduce the disk abundances; any higher and the infalling gas would be more metal-rich than the most metal-poor thin disk stars. This model results in very similar [O/Fe] distributions to the $y/Z_\odot=1$ case. We assume that the infalling gas has $\mathOFe=0$ at all times; an alternate run with $\mathOFe=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations. In summary, pre-enriched gas infall may be necessary for the two-infall model to match the observed [O/Fe] distribution across the disk.

@@

\begin{figure*}
    \centering
    \includegraphics{figures/abundance_evolution_params.pdf}
    \caption{Stellar age--abundance relations produced by select multi-zone models with \yZ{1}. The layout is similar to Figure \ref{fig:abundance-evolution-yields}. Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.48$. {\bf Key takeaway:} Model (d) comes the closest to the observed age--metallicity relation at the expense of the age--[O/Fe] relation, but no model completely reconciles the dilution problem.}
    \label{fig:abundance-evolution-params}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.9\linewidth]{figures/mdf_evolution.pdf}
    \caption{Evolution of the MDF across the Galactic disk. Each panel presents normalized stellar [Fe/H] distributions within a {2 kpc}-wide annulus, and the distributions are binned by stellar age. Rows (a) and (b) present the distributions from multi-zone GCE models, while row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}). A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}. The vertical blue dotted lines in row (c) mark the mode of the distribution in the $1-2\,{\rm kpc}$ age bin for reference. Also in row (c), the gray dashed line marks the cut at $\mathFeH>-0.4$ for upper red giant branch and red clump stars, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages. Distributions in all panels are restricted to $0\leq|z|<0.5\,{\rm kpc}$ and boxcar-smoothed with a width of {0.1 dex} for visual clarity. {\bf Key takeaway:} The APOGEE data show remarkably little variation in the mode at all radii over the past $\sim6-8$ Gyr, while both GCE models produce a steady evolution toward higher [Fe/H] with time.}
    \label{fig:mdf-evolution}
\end{figure*}

>>>>

\begin{abstract}
    Stellar populations in the Milky Way exhibit a clear separation into two chemically distinct populations that are separated by their [$\alpha$/Fe] ratios. This $\alpha$-bimodality is not a universal feature of simulated disk galaxies and may point to the Milky Way's unique evolutionary history. A popular explanation for this observation is the two-infall scenario, which postulates that two periods of substantial accretion rates dominate the assembly history of the Galaxy. However, most previous studies using the two-infall scenario have explored a limited portion of the parameter space, typically neglecting radial migration and assuming that the Galactic disk never ejected a substantial outflow. Thanks to advances in stellar age measurements in recent years, we can now also compare this popular model to more direct measurements of the Galaxy's evolutionary timescales across the disk from large stellar catalogs. We run multi-zone galactic chemical evolution (GCE) models with a two-infall-driven star formation history, radially dependent mass-loaded outflows, and a prescription for radial migration tuned to a hydrodynamic simulation. We compare our model results to abundance patterns across the disk from APOGEE DR17,
    % and early data from the SDSS-V Milky Way Mapper program,
    supplemented with stellar age estimates through multiple methods. Although the two-infall scenario offers a natural explanation for the [$\alpha$/Fe] bimodality, it struggles to explain several features of the age--abundances structure in the disk. The two-infall scenario generically predicts a massive and long-lasting dilution event, but the data show that stellar metallicity is remarkably constant with age across much of the Galactic disk. This apparent age-independence places considerable restrictions upon the two-infall parameter space. These issues can be mitigated, but not completely resolved, by allowing the accreted gas to be pre-enriched to low metallicity.
\end{abstract}

@@

% \todo{Hook, summary of alpha-bimodality.}
Studies of galactic chemical evolution (GCE) aim to explain observed stellar abundance patterns by modeling the star formation history of the Milky Way. A long-standing paradigm of GCE has been that the metallicity of the interstellar medium (ISM) increases over time due to supernova enrichment from successive generations of stars. In this view, one feature of the Milky Way disk that is difficult to explain is the so-called ``$\alpha$-bimodality'': the presence of two populations of stars at similar metallicity but separated by their \aFe ratio \citep[e.g.,][]{bensby_exploring_2014}. The high-$\alpha$ sequence consists of old stars \citep[$\gtrsim9$ Gyr;][]{pinsonneault_apokasc-3_2025} with super-Solar \aFe and is associated with the kinematic thick disk \citep[e.g.,][]{fuhrmann_nearby_1998}, while the low-$\alpha$ sequence is younger, with approximately Solar \aFe, and is associated with the thin disk. The $\alpha$-bimodality is present across the Galactic disk, but the relative strength of the high- and low-$\alpha$ sequences varies by location \citep{hayden_chemical_2015}.

An explanation for the $\alpha$-bimodality has yet to be broadly accepted in the GCE community \todo{(reword)}. An $\alpha$-bimodality is not a universal feature in simulated Milky Way-mass galaxies \todo{(citations; also mention external galaxies?)}, so its presence and characteristics in our own galaxy may provide clues to its unique evolutionary history. GCE models that attempt to solve this problem generally fall into two camps: some explain the $\alpha$-bimodality as a result of secular processes, such as the radial migration of stars and the inside-out growth of the disk \todo{(citations)}; others argue that the two sequences point to a bursty star formation history, perhaps driven by multiple discrete accretion events \todo{(citations)} or a change in the star formation efficiency \citep[e.g.][]{conroy_birth_2022}.

% Summary of two-infall literature
The two-infall model of chemical evolution was proposed by \citet{chiappini_chemical_1997} to explain the origin of the high- and low-$\alpha$ disks. Though the model has been revised and refined since, the basic premise remains the same: the rate of gas infall onto the Galaxy is described by two consecutive, exponentially declining bursts. The relatively low infall rate between the two bursts leads to a hiatus in the star formation rate, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences without producing many stars in between. 
% By varying the timescale of the second infall, the model can produce inside-out disk growth and a radial abundance gradient.
The initial model of \citet{chiappini_chemical_1997} successfully reproduced the available abundance data at the time, which were largely confined to the Solar neighborhood.

Subsequent studies refined the two-infall model to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}. Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, a variable star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations due to spiral modes \citep{spitoni_2d_2019}, and pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024} in a two-infall context. Recently, \citet{spitoni_beyond_2023} and \citet{palla_mapping_2024} proposed a third gas accretion event in the last $\sim3$ Gyr to match the inferred star formation history from {\it Gaia} \citep{ruiz-lara_recurrent_2020} and explain the recent abundance evolution of the Solar neighborhood.

% \todo{Observational evidence other than $\alpha$-bimodality.} 
The chemical and kinematic separation of the high- and low-$\alpha$ disks remains the primary observational evidence behind the two-infall model. \citet{spitoni_remind_2024} argued that the gap between the sequences in \aFe, contrasted with their overlap in $[\alpha/{\rm H}]$, supports a haitus in star formation which is a natural consequence of the two-infall model. \citet{nissen_high-precision_2020} measured abundances and estimated ages for nearby Solar-type stars and reported two sequences in the age--metallicity distribution which could be explained by the two-infall model \todo{(rewrite)}. \citet{nataf_accurate_2024} also observe multiple sequences in the age--metallicity relation in their sample of $\sim400,000$ local subgiants, although the break between them is not as clean as in \citet{nissen_high-precision_2020}. \citet{chen_recent_2025} however argue that this trend can be explained by a smooth star formation history with inside-out growth: the older sequence consists of stars which have migrated from the inner galaxy, where the star formation rate peaked early, while the younger sequence was formed locally.

@@

% \todo{Goal and summary of paper.} 
We run multi-zone GCE models with a two-infall accretion history, radially-dependent mass-loaded outflows, and a prescription for radial migration tuned to a hydrodynamical simulation. We investigate the impact of the scale of SN yields and outflows, the strength of radial migration, the enrichment of the circumgalactic medium, and the local disk mass surface density ratio on the GCE model predictions. We compare our results to abundance distributions across the disk from APOGEE DR17, and to age--abundance relations from multiple age catalogs. We describe our observational sample in Section \ref{sec:observational-sample}, and we detail our chemical evolution models and parameter selection in Section \ref{sec:methods}. We compare our multi-zone model predictions to the data in Section \ref{sec:multizone-results}. We discuss in Section \ref{sec:discussion} and conclude in Section \ref{sec:conclusions}.

@@

The infall rate is described by two successive, exponentially declining bursts in time. The first infall component induces the formation of the thick disk, and the second component produces the thin disk. At a given galactocentric radius $R_{\rm gal}$, the un-normalized form of the infall rate is
\begin{equation}
    \label{eq:twoinfall-ifr}
    f_{\rm in}(t|R_{\rm gal}) = e^{-t/\tau_1} + f_{2/1}(R_{\rm gal}) e^{-(t-t_{\rm max})/\tau_2},
\end{equation}
where $\tau_1$ and $\tau_2$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall and thus the time of maximum gas infall, and $f_{2/1}$ is the ratio of the second infall amplitude to the first. We calculate $f_{2/1}$ for each zone such that the resulting stellar density profile follows a two-component disk, with the surface density ratio of the thick and thin disks given by
\begin{equation}
    f_\Sigma(R) \equiv \frac{\Sigma_1(R)}{\Sigma_2(R)} = f_{\Sigma,0} e^{R(1/R_2 - 1/R_1)}.
\end{equation}
We adopt a thick disk scale radius of $R_1=2.0\,{\rm kpc}$, a thin disk scale radius of $R_2=2.5\,{\rm kpc}$, and a central surface density ratio of $f_{\Sigma,0}=0.27$ \citep{bland-hawthorn_galaxy_2016}. In the Solar neighborhood, this produces a thick-to-thin disk mass ratio of $f_\Sigma(R_\odot)=0.12$. By comparison, \citet{mackereth_age-metallicity_2017} finds $f_\Sigma(R_\odot)=0.18\pm0.05$ from APOGEE. \citet{fuhrmann_local_2017} derive $f_\Sigma(R_\odot)=0.57$ from a very small volume (25 pc radius). \todo{Compare with other two-infall papers, which generally have a higher thick-to-thin ratio.} \citet{spitoni_galactic_2020} explores $f_\Sigma(R_\odot)\approx0.23-0.31$, \citet{palla_chemical_2020} assumes $f_\Sigma(R_\odot)=0.23$, \citet{spitoni_apogee_2021} derives $f_\Sigma(R_\odot)=0.18$ (again from APOGEE), \citet{spitoni_remind_2024} assumes $f_\Sigma(R_\odot)=0.4$.

@@

The two-infall model generically predicts {\it three} peaks in the [O/Fe] distribution which correspond to the high-$\alpha$ sequence, the abundance ``turn-over'' after the second infall, and finally the late-time low-$\alpha$ sequence. Figure \ref{fig:ofe-distribution-yields} compares [O/Fe] distributions from across the Galactic disk produced by models with the \yZ{1} and \yZ{2} yield sets. For model (a) with $y/Z_\odot=1$, the two thin disk peaks are close enough together that they approximate a single peak, especially once observational uncertainties are factored in. With the \yZ{2} yield set, however, there is a $\sim0.2$ dex separation between the low- and intermediate-$\alpha$ peaks thanks to increased efficiency of CCSN element production. As a result, model (b) predicts a high density of stars at $\mathOFe\approx+0.2$ where the data show a relatively low density.

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_params.pdf}
    \caption{Stellar [O/Fe] distributions produced by select multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e). The layout is similar to Figure \ref{fig:abundance-evolution-yields}. Each column shows results from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$ (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$. {\bf Key takeaway:} For the \yZ{2} case, pre-enrichment of the accreted gas or a higher thick-to-thin disk ratio can improve the low-$\alpha$ distribution while preserving the high-$\alpha$ peak.}
    \label{fig:ofe-distribution-parameters}
\end{figure*}

In Figure \ref{fig:ofe-distribution-parameters}, we show the result of our attempts to mitigate the intermediate-$\alpha$ peak discrepancy for the \yZ{2} yield set in a few different ways, namely by reducing the size of the thin disk loop seen in panel (b) of Figure \ref{fig:ofe-feh-density}. First, we substitute our fiducial SN Ia DTD with a simple power-law,
\begin{equation}
    f_{\rm Ia}^{\rm plaw}(t) = (t/1\,\rm{Gyr})^{-1.1},
    \label{eq:powerlaw-dtd}
\end{equation}
which reduces the median SN Ia delay time from $\sim2\,{\rm Gyr}$ to $\sim0.5\,{\rm Gyr}$. As shown in column (b), this has the intended effect on the low-$\alpha$ sequence, but it also entirely eliminates the high-$\alpha$ peak. \citet{dubay_galactic_2024} discuss in detail why such a DTD is disfavored by Milky Way stellar abundances, and their results hold true for the two-infall model as well.
% In columns (c) and (d) of Figure \ref{fig:ofe-df}, we attempt to mitigate the issue of the intermediate-$\alpha$ peak for the $y/Z_\odot=2$ yield set. Model (c) switches out our fiducial DTD with a power-law DTD, which decreases the timescale for Fe production. However, as shown by \citet{dubay_galactic_2024}, models with a power-law DTD struggle to reproduce the high-$\alpha$ sequence for a wide range of star formation histories, and the results are no different for this two-infall model.

Next, in model (c) the metallicity of the infalling gas increases to $\mathXH_{\rm CGM}=-0.5$ at late times. We choose this value because it is the maximum which can plausibly still reproduce the disk abundances; any higher and the infalling gas would be more metal-rich than the most metal-poor thin disk stars. This model results in very similar [O/Fe] distributions to the $y/Z_\odot=1$ case. We assume that the infalling gas has $\mathOFe=0$ at all times; an alternate run with $\mathOFe=+0.3$ shifted the distribution towards higher [O/Fe], worsening agreement with observations. 
% In summary, pre-enriched gas infall may be necessary for the two-infall model to match the observed [O/Fe] distribution across the disk.

Finally, in model (d) we increase the local thick-to-thin disk surface density ratio by a factor of 4 to $f_\Sigma(R_\odot)=0.5$. This value means that 1 in 3 stars in the Solar annulus belong to the thick disk and is on the high end of estimates \todo{(citations)}. The result as shown in Figure \ref{fig:ofe-distribution-parameters} is a true bimodal abundance distribution, with a more prominent high-$\alpha$ peak than in the previous models. \todo{Note that APOGEE high-$\alpha$ sequence is over-emphasized by survey selection function.} In summary, either pre-enriched infall or an enhanced disk mass ratio can improve agreement with the observed thin disk abundances for the \Z{2} case. These parameters also help the model better fit the age--metallicity relation, as shown in Section \ref{sec:age-abundance} for the \yZ{1} case.

@@

\begin{figure*}
    \centering
    \includegraphics{figures/abundance_evolution_params.pdf}
    \caption{Stellar age--abundance relations produced by select multi-zone models with \yZ{1}. The layout is similar to Figure \ref{fig:abundance-evolution-yields}. Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$. {\bf Key takeaway:} Model (d) comes the closest to the observed age--metallicity relation at the expense of the age--[O/Fe] relation, but no model completely reconciles the dilution problem.}
    \label{fig:abundance-evolution-params}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.9\linewidth]{figures/mdf_evolution.pdf}
    \caption{Evolution of the MDF across the Galactic disk. Each panel presents normalized stellar [Fe/H] distributions within a {2 kpc}-wide annulus, and the distributions are binned by stellar age. Rows (a) and (b) present the distributions from multi-zone GCE models with different yield scales. For both models we adopt the following non-fiducial parameters: $\mathFeH_{\rm CGM}=-0.7$, $\sigma_{\rm RM8}=3.6$ kpc, and $f_\Sigma(R_\odot)=0.25$. A Gaussian scatter has been applied to each model stellar population in rows (a) and (b) according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}. Row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}). The vertical blue dotted lines in row (c) mark the mode of the distribution in the $1-2\,{\rm kpc}$ age bin for reference. Also in row (c), the gray dashed line marks the cut at $\mathFeH>-0.4$ for upper red giant branch and red clump stars, and the gray solid line marks the cut at $\mathFeH<+0.45$ for all stars with [C/N]-based ages. Distributions in all panels are restricted to $0\leq|z|<0.5\,{\rm kpc}$ and boxcar-smoothed with a width of {0.1 dex} for visual clarity. {\bf Key takeaway:} The APOGEE data show remarkably little variation in the mode at all radii over the past $\sim6-8$ Gyr, while both GCE models produce a steady evolution toward higher [Fe/H] with time.}
    \label{fig:mdf-evolution}
\end{figure*}
